Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2015-04-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Update figures, add HF NG figures, update plotting script and latex.

\begin{figure}[ht!]
	\centering
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0p61m_Reps_Avg}
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0p31m_Reps_Avg}\\
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0p15m_Reps_Avg}
	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0m_Reps_Avg}\\
	\caption[Heat flux at the wall along the centerline of the natural gas fueled burner]{Heat flux at the wall along the centerline of the natural gas fueled burner. The heat fluxes are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall. Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
	\label{HF_Center_TWNG_comp}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0p61m_Reps_Avg}
	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0p31m_Reps_Avg}\\
	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0p15m_Reps_Avg}
	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0m_Reps_Avg}\\
	\caption[Heat flux at the wall along the edge of the natural gas fueled burner]{Heat flux at the wall along the edge of the natural gas fueled burner. The heat fluxes are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall. Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
	\label{HF_Edge_TWNG_comp}
\end{figure}

>>>>

\begin{figure}[ht!]
	\centering
	\includegraphics[width=2.5in]{../Figures/TWNG01_HF_Center_Avg}
	\includegraphics[width=2.5in]{../Figures/TWNG03_HF_Center_Avg}\\
	\includegraphics[width=2.5in]{../Figures/TWNG05_HF_Center_Avg}
	\includegraphics[width=2.5in]{../Figures/TWNG07_HF_Center_Avg}\\
	\caption[Heat flux at the wall along the centerline of the natural gas fueled burner]{Heat flux at the wall along the centerline of the natural gas fueled burner. The heat fluxes are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall. Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
	\label{HF_Center_TWNG_comp}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=2.5in]{../Figures/TWNG01_HF_Offset_Avg}
	\includegraphics[width=2.5in]{../Figures/TWNG03_HF_Offset_Avg}\\
	\includegraphics[width=2.5in]{../Figures/TWNG05_HF_Offset_Avg}
	\includegraphics[width=2.5in]{../Figures/TWNG07_HF_Offset_Avg}\\
	\caption[Heat flux at the wall along the edge of the natural gas fueled burner]{Heat flux at the wall along the edge of the natural gas fueled burner. The heat fluxes are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall. Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
	\label{HF_Edge_TWNG_comp}
\end{figure}
